\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-04-09 Latex/paper-resum.tex
Add Thanks to ...
Add Thanks to ..
Styling
Styling

@@

%\TODO{Remove ToC in final version}
%\tableofcontents
%\clearpage

@@

To introduce a general idea of the method, let us define the process $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$, but we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
\end{equation}
The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest. 
\subsection{FRAs Vs futures}
 The cash flows in FRAs and futures are computed under different measures. Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes. As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
\begin{equation}\label{forward_rate}
L_{E}(t_0, t_1, t_2) = \frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)
\end{equation} 
where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. we must note, that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
\end{equation*}
And $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0) \quad \text{when} \quad t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty \quad \text{when} \quad t_0 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs. It is common in the market to find two version of these futures, depending on how the fixings of the refrence index are using. Given $t_0 < t_1$, we will define the overnight compounding rate as
\begin{equation*}
R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
\end{equation*}
and the overnight average rate as
\begin{equation*}
R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{equation*}
We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right), \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), \quad t \in [0,t_0] \\
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
Then the convexity adjustment for $ R(t_0,t_1)$ is
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
\end{equation}
The second observation is that we have the following equivalence
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  \end{equation}
In order, to clarify the convexity expression and the calculations, we will define 
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
\end{equation*}

\begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for OIS futures is 
\begin{equation}\label{convexity_ois_future}
\bar{R}(t_0,t_1) = \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}} + E(t_0)
\end{equation}
and for the average OIS future is
\begin{equation}\label{convexity_avg_ois_future}
\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
\end{equation}
\end{theorem}
where  $\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$, and $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0) \quad \text{when} \quad t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty \quad \text{when} \quad t_0 \to \infty$.
\begin{proof}
See appendix \ref{Proof_CA_OIS_futures}.
\end{proof}

@@

\begin{remark}
We can calculate the convexity adjustment for the case $t_0 < t < t_1$ in a similar way to when $t < t_0$, for this we will define
\begin{equation*}
I(t,t_1):=\int_{t}^{t_1} r_s ds
\end{equation*}
and 
\begin{align*}
R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1\right), \\
R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
\end{align*}
\end{remark}

\begin{example}[Convexity adjustment for OIS futures under the Hull-White model]\label{example_convexity_hw_ois}
Similarly to the Example \ref{example_ca_future}, we can find the equivalent parameters for the Hull-White model: 
\begin{align*}
\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  \right).
\end{align*}
Therefore, we have that
\begin{align*}
\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
&= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
&+ \frac{\sigma^{2}}{2k^2} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k(t_1 - s))\right)^{2} ds\\
&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
\end{align*}
Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.\\

>>>>

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

@@

%\TODO{Remove ToC in final version}
%\tableofcontents
%\clearpage
\blfootnote{The authors would like to thank Elisa Al\`os for helpful discussions.}

@@

To introduce a general idea of the method, let us define the process $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$, but we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$, where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left[f(x_t)\right] + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left[ f(x_t) \right] = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left[\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] \lambda_s ds \right]. 
\end{equation}
The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest. 
\subsection{FRAs Vs futures}
 The cash flows in FRAs and futures are computed under different measures. Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes. As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
\begin{equation}\label{forward_rate}
L_{E}(t_0, t_1, t_2) = \frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)
\end{equation} 
where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. we must note, that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E[t_0]. 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
\end{equation*}
and $\|E\left[t_0\right]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left[t_0\right]\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs. It is common in the market to find two version of these futures, depending on how the fixings of the refrence index are using. Given $t_0 < t_1$, we will define the overnight compounding rate as
\begin{equation*}
R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
\end{equation*}
and the overnight average rate as
\begin{equation*}
R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{equation*}
We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R(t_0,t_1)  \right], \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R_{avg}(t_0,t_1)  \right].
\end{align*}
Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
&= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
%\end{align*}
\intertext{and when $t \in  [t_0, t_1]$, we have}
%\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
 &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
\end{align*}
Then the convexity adjustment for $ R(t_0,t_1)$ is
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
\end{equation}
The second observation is that we have the following equivalence
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
In order, to clarify the convexity expression and the calculations, we will define 
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
\end{equation*}

\begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for OIS futures is 
\begin{equation}\label{convexity_ois_future}
\bar{R}(t_0,t_1) = \frac{1}{\delta_{t_0,t_1}}\left(\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right) - 1\right) + E[t_0],
\end{equation}
and for the average OIS future is
\begin{equation}\label{convexity_avg_ois_future}
\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] }{\delta_{t_0,t_1}} \approx \frac{1}{\delta_{t_0,t_1}}\left(\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] \right) - \frac{1}{2}\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds\right)
\end{equation}
where  
\begin{equation}
\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du, 
\end{equation}
and $\|E[t_0]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E[t_0]\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_OIS_futures}.
\end{proof}

@@

\begin{remark}
We can calculate the convexity adjustment for the case $t_0 < t < t_1$ similarly to when $t < t_0$. For this, we will define
\begin{equation*}
I(t,t_1):=\int_{t}^{t_1} r_s ds
\end{equation*}
and 
\begin{align*}
R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1\right), \\
R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
\end{align*}
\end{remark}

\begin{example}[Convexity adjustment for OIS futures under the Hull-White model]\label{example_convexity_hw_ois}
Similarly to the Example \ref{example_ca_future}, we can find the equivalent parameters for the Hull-White model: 
\begin{align*}
\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\biggl(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\biggr),\\
\mathbb{E}^{\mathbb{Q}}\left[I(t_0,t_1)\right]&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\\
& \text{ }\text{ }\text{ }+ \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  \right).
\end{align*}
Therefore, we have that
%\begin{align*}
%\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
%&= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
%&+ \frac{\sigma^{2}}{2k^2} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k(t_1 - s))\right)^{2} ds\\
%&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
%&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
%\end{align*}
\begin{align*}
\frac{1}{2}\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds &= \frac{\sigma^{2}t_0}{2k^{2}} \biggl( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \biggr)\\  
&+ \frac{\sigma^{2}}{2k^{2}} \biggl(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt_0)t_0 \\
&\quad - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \biggr).
\end{align*}
Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.\\
